Methods

### 2019-01-24 Methods.Rmd
Individual plots

site.names <- list("Port Nolloth", "Lamberts Bay", "Saldanha Bay", "Yzerfontein")
for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = site.names[i])
  }

plot_fun <- function(x) {
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = attributes(x)$ref)
  }

# ... apply the function
#op <- par(no.readonly = TRUE)
par(mfrow = c(2, 2),
    mar = c(2.5, 3.5, 2.5, 0.5),
    mgp = c(2.5, 1, 0),
    oma = c(0, 0, 1, 0))
l_ply(PN_wave, plot_fun)
#par(op)

# Save each of the graph seperate- graph PN, LB, saldanha Bay and Yzerfontein
```

>>>>

# RWS: The order of these sites was incorrect
# Rather get the names from the pre-existing data
# site.names <- list("Port Nolloth", "Lamberts Bay", "Saldanha Bay", "Yzerfontein")

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}

# x <- PN_wave[[3]]

plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures/",plot_name,"_wavelet.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}

ldply(PN_wave, plot_fun)

# ... apply the function
#op <- par(no.readonly = TRUE)
# par(mfrow = c(2, 2),
#     mar = c(2.5, 3.5, 2.5, 0.5),
#     mgp = c(2.5, 1, 0),
#     oma = c(0, 0, 1, 0))
#par(op)

# Save each of the graph seperate- graph PN, LB, saldanha Bay and Yzerfontein
# l_ply(PN_wave, plot_fun)
```
